---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# uglycat
[![Travis-CI Build Status](https://travis-ci.org/dcgerard/uglycat.svg?branch=master)](https://travis-ci.org/dcgerard/uglycat)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/dcgerard/uglycat?branch=master&svg=true)](https://ci.appveyor.com/project/dcgerard/uglycat)
[![Coverage Status](https://img.shields.io/codecov/c/github/dcgerard/uglycat/master.svg)](https://codecov.io/github/dcgerard/uglycat?branch=master)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)


The goal of uglycat is to account for uncertainty in genotype estimates in polyploids when estimating linkage disequilibrium.

# Installation

To install, use the [devtools](https://cran.r-project.org/package=devtools) package:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github(repo = "dcgerard/uglycat")
```

# Citation

To cite package 'uglycat' in publications use:

>>> David Gerard (2018). uglycat: Using Genotype Likelihoods Yields Correlations and T-statistics. R package version 0.0.0.9000. URL [https://github.com/dcgerard/uglycat](https://github.com/dcgerard/uglycat).

A BibTeX entry for LaTeX users is

```{tex}
@Manual{gerard2018uglycat,
  title = {uglycat: Using Genotype Likelihoods Yields Correlations and {T}-statistics},
  author = {David Gerard},
  year = {2018},
  note = {R package version 0.0.0.9000},
  url = {https://github.com/dcgerard/uglycat}
}
```

# Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
